Turbulence in compact to giant HII regions

### 2021-10-28 strucfunc_paper.tex
Use the new strucfunc figures in the paper
But I am not happy with the layout yet.

We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions. 
Table \ref{tab:Reg} shows the HII regions names
with the main physical properties of each region. 
These regions are located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.

@@

Orion is a galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.

We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. The data were obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory. These observation cover 3 \(\times\) 5 arcmin\(^{2}\)of the Orion nebula and the data consist of 96, 300 arcsec North-South orientated slits at 2 arcsec intervals with a width of 0.8 arcsec. The velocity resolution is 8 km s\(^{-1}\).

The Carina nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
The stellar content has lead to identify the Carina nebula as a star formation region, and as such it presents several phenomena related with young stras as (\citet{2006ApJ...644.1151S} and reference therein): evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some. 
All of these phenomena are consequence of the UV radiation and stellar winds from star clusters in the HII region.

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR. A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}.

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
The ESO VLT/FLAMES multi-fiber spectograph was used for observations (Gaia-ESO Survey internal release \(iDR4\)) of Lagoon nebula  and Carina nebula \citep{2002Msngr.110....1P}. 
Mainly the spectra were obtained with the Giraffe HR15N setup (\(R \sim19 000\), wavelength range 6444-6818 A) which allow to observe \halpha\ emission line. 
The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.

Using observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30 Doradus).
This nebula us located in the LMC (Large Magellanic Cloud) at a distance of 49.9 kpc \citep{2013Natur.495...76P} and is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
It host the star forming region NGC 2070 that contains the massive star cluster R136.
NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT). 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 60 kpc. 
It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars. 
This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.

\subsection{Regions in M33 and NGC 6822}

NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.

The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
 The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.
\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.

NGC 595 is the second brightest giant HII region in the M33 galaxy.
The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.

It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{1996AJ....112.1928G} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.

%Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX. HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.

The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
The cumulative integration time per frame is 36 s with a seeing value of 1''.
The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

%\citet{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08

\begin{table*}
\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
\begin{tabular}{ccccccccc}\hline
HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

@@

\subsection{The second order structure function}

One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.

The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:

\begin{equation}\label{eq:S}
B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
\end{equation}

where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

We also use the functional form of the structure function:

\begin{equation}\label{eq:b}
b(r)=2[1-C(r)]\zeta+\eta
\end{equation}

where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.

\subsection{Application to our HII regions sample}\label{sec:apply}

The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}. 
In this way we avoid one fundamental problem in the interpretation of the structure function results. The slope in the majority of previous studies and hence, the correlation length, is obtained by eye. 
The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
If this increase in values is stopped it is commonly assumed that one particular range has been found. 
In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
This way we can maintain consistency in our analysis.

@@

The Figure \ref{fig:hist} shows the histograms of each individual sample with the variance  \(\sigma^{2}\), along the number of points of each sample.

@@

Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
The third column is the correlation length \(r_0\).
The index \(m\) is shown in the forth column;
this index is used as a reference for comparison between theory and observations.
In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.

@@

The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
NGC 346 correlation length is 1.4 pc and its index is 1.13.

The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}. It is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}, we use this combined sample for the structure function analysis.
Carina has an index of 0.82 with a correlation length of 0.94 pc.
The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.

For Orion we have the opportunity to study two different observations. \citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc. Large scales results shows an index of 0.9 with a correlation length of 0.84 pc while the small scales have 1.44 and 0.062 pc.

The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).

>>>>

We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
Table \ref{tab:Reg} shows the names with the main physical properties of each region.

@@

Orion (M42) is the prototype galactic HII region and one on the best objects studied in the sky.
Located at a distance of 440 pc \citep{2008AJ....136.1566O} its main physical and kinematics properties, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region. Some of these young stars are accountable for stellar jets and Herbig-Haro objects seen in the nebula \citep{arthur2016turbulence}.

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citep{2006ApJ...644.1151S}.
Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
As a star formation region,it presents several phenomena related with young stars as: evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some, \citet{2008hsf2.book..138S} and reference therein.
An approaching and receding kinematics components are known in the nebula.

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR. A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

The Tarantula Nebula (30 Doradus) is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}. The nebula is located at a distance of 49.9 kpc \citep{2013Natur.495...76P}.
It host the star forming region NGC 2070 that contains the massive star cluster R136. 
The star formation rate gas increased recently, 1-3 Myr ago \citep{2016ApJ...833..154C}, and the central ionized region spans for 40 pc.
This nebula is used as a comparison for extragalactic star-forming regions.

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citep{2001ApJ...562..303D}. 
It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars. 
This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.

The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
%HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
%HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
%Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX. HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.

%NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
%It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
%It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
%The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
%Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
%\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
%The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
%This suggest that two episodes of star formation, at least, have taken place in the GEHR.
%\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.

%NGC 595 is the second brightest giant HII region in the M33 galaxy.
%The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
%\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
%\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
%It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

\subsection{Observations}

We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. 
The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).

Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s. 
The table 1 on their work summarize the propertie of each field.
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
The cumulative integration time per frame is 36 s with a seeing value of 1''.
The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}. The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

\begin{table*}
\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
\begin{tabular}{ccccccccc}\hline
HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
NGC 604 &820$\pm$30  & 400    &   39.65    & 0.011 & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
NGC 595 &820$\pm$30  & 400    &   39.36    & 0.009 & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
Hubble X  &   490$\pm$40  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
Hubble V  &   490$\pm$40  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
30 Dor    &   49.97$\pm$0.19    & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
Carina    &   2.35$\pm$0.05  & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
NGC 346   &   61.9$\pm$1.1 & 64      &    38.67     & 0.0021   & 100&    &     & \\
Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
Orion     &   0.436$\pm$0.02  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

%2013ApJ...773...69G M33 dist

@@

%\subsection{The second order structure function}

%One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
%They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
%By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.

%The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:

%\begin{equation}\label{eq:S}
%B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
%\end{equation}

%where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.

%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
%This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
%In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

%We also use the functional form of the structure function:

%\begin{equation}\label{eq:b}
%b(r)=2[1-C(r)]\zeta+\eta
%\end{equation}

%where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
%The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
%The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
%In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.

%\subsection{Application to our HII regions sample}\label{sec:apply}

%The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}. 
%In this way we avoid one fundamental problem in the interpretation of the structure function results. The slope in the majority of previous studies and hence, the correlation length, is obtained by eye. 
%The traditional way to find it is to determine a particular range of ascending values in the structure function results. %If this increase in values is stopped it is commonly assumed that one particular range has been found. 
%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
%Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
%This way we can maintain consistency in our analysis.

@@

The Figure \ref{fig:hist}....

@@

Figure \ref{fig:SFs}...

Table \ref{tab:Res}...

%Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
%The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
%The third column is the correlation length \(r_0\).
%The index \(m\) is shown in the forth column;
%this index is used as a reference for comparison between theory and observations.
%In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
%Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.

@@

%The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
%For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
%For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
%The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
%NGC 346 correlation length is 1.4 pc and its index is 1.13.

%The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}. It is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}, we use this combined sample for the structure function analysis.
%Carina has an index of 0.82 with a correlation length of 0.94 pc.
%The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.

%For Orion we have the opportunity to study two different observations. \citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc. Large scales results shows an index of 0.9 with a correlation length of 0.84 pc while the small scales have 1.44 and 0.062 pc.

%The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
%This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
%NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
%Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
%Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
  \label{fig:strucfunc-fit-A}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
  \label{fig:strucfunc-fit-B}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
  \label{fig:strucfunc-fit-C}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
\end{figure*}
